Automatic detection of bad habits of programming in Scratch

### 2014-04-17 paperFIE_en.tex
Conclussions section refined

\paragraph{} --Sin retocar--Regarding the named object is curious that other users Scratch named correctly, ie, significantly, the variables used in their projects. In our opinion this is because when you create a variable is mandatory to assign a name, because the environment does not name by default. However, when creating a new character is asinga named \textit{SpriteX} automatically. Maybe a change of environment that requires the user to name the new objects eliminate this malpractice.
\paragraph{} --Sin retocar-- Regarding the code repetition and low usage users Scratch make the definition of own blocks (the equivalent of creating methods or procedures in other languages), you may work as performed by Seiter and Foreman \cite {seiter2013modeling} in which shows the capacity for abstraction and modularization are concepts that seem habilidadades develop from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 \footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate this line to continue advancing in the definition of an appropriate framework for different ages and to check whether users online learning and those who do in a regulated environment show rates than use this functionality .

>>>>

\paragraph{}Regarding the named object it is curious that Scratch users name correctly, ie significantly, the variables used in their projects. In our opinion the reason to explain this paradox is because it is mandatory to assign a name to a variable the moment it is created, as the environment does not name it by default. However, when creating a new character a  \textit{SpriteX} name is assigned automatically. A change on this feature of the environment, obliguing users to name new objects, would eliminate this malpractice.
\paragraph{}Regarding the code repetition and low usage Scratch users make of creating their own blocks (the equivalent of defining methods or procedures in other languages), works as the one performed by Seiter and Foreman \cite {seiter2013modeling}, in which they show that abstraction and modularization capacities are concepts that seem to be developed from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 years old \footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate this line to continue advancing in the definition of an appropriate framework for different ages and to check whether users learning online and those who do it in a regulated environment show different use rates of this functionality .
